---
title: "Data 607 Assignment 5"
author: "Melissa Bowman"
date: "2022-10-14"
output: html_document
---

In Assignment 5, three different files where separately created in a text editor. These files were HTML (using an html table), XML, and JSON formats. The files were then uploaded to a GitHub repository when the files were transformed into data frames using R. 

### Reading a JSON file from URL then creating a Data Frame. 
```{r json_data_frame}

#Library used
library(jsonlite)

# A function in jsonlite fromJSON converts JSON content to R objects. 
json_data = fromJSON("https://raw.githubusercontent.com/melbow2424/Data-607-Assignment-5/main/books.json")
```
### Reading a XML file from URL then creating a Data Frame. 
```{r xml_data_frame}
#Libraries used
library(XML)
library(plyr)
library("xml2")

#Reads XML file from the xml2 package 
xml_file <- read_xml("https://raw.githubusercontent.com/melbow2424/Data-607-Assignment-5/main/books.xml")

# Could not get the XML file directly from the url reading so parse the info.
xml_format <- xmlParse(file = xml_file)

#Idply for every element in a list, a function is applied, here xmlToList and data.frame, and then a data frame is created. xmlToList function creates a list from xml nodes.
xml_data <- ldply(xmlToList(xml_format), data.frame)
```
### Reading a HTML file from URL then creating a Data Frame. 
```{r html_data_frame}

library(rvest)
library(RCurl)
library(data.table)

#Downloads the url from the RCurl package 
html_file <- getURL('https://raw.githubusercontent.com/melbow2424/Data-607-Assignment-5/main/books.html')

#Reads data from HTML tables (if formatted as an HTML table). Comes from XML package. This created a list.
tables = readHTMLTable(html_file, as.data.frame = TRUE)

#From that list I used rbindlist to create a data table
html_data <- rbindlist(tables)
```
### Viewing all Data frames: 
```{r print_data_frame}
print(json_data)

print(xml_data)

print(html_data)
```
### Conclusion: 

Each file needed to be imported into R differently due to the structure of each file. Also, each data frame did not create identical layouts. The json data frame split the two authors from the R for Data Science by a comma where the xml created new columns for the two authors names. The html data frame had the two authors from the R for Data Science book separated by a | but that was written into the file. That had nothing to do with the R coded inputs. 


